Argumentation theory for mathematical argument\thanks{Support from the UK Engineering and Physical Sciences Research Council is acknowledged under grants EPSRC EP/K040251/2 (Corneli, Martin and Nesin), EP/J017728/2 (Murray-Rust) and EP/P017320/1 (Pease).}

### 2018-07-11 main.tex
minor

The data that underlie this section were generated in a series of online experiments in collaborative problem solving convened by mathematician Terence Tao \citeyearpar{tao2009imo,tao2011imo}.
\thesis{We use IATC to expand on the analysis of
  this data presented by \citet{pease-and-martin},} showing how IATC can
advance the theory of mathematical argument through the
detailed analysis of real world examples, as per \citet{Carrascal2015}.

In the earlier analysis, Pease and Martin took a broad stroke approach, with each
comment comprising a single unit to be tagged.  They developed a typology
of five intuitive comment types, based on the mathematical content of each
comment: \emph{examples},
\emph{conjectures},
\emph{concepts},
\emph{proofs},
and \emph{other}. 
%%
In order to assign comments to these categories, both authors
performed close content analysis, together, on all comments posted
between the time at which Tao posted the problem to his blog
(8pm, UTC on July 19th, 2011) and the time he posted
that it had been solved (9.50pm, UTC on July 19th, 2011).
The discussion comprised 147 comments over 27 threads.
%%
Ten comments were assigned to more than one category.
(Both authors have a first degree in
Mathematics; one of us has a PhD in Mathematics and over 10 years
experience as a professional research mathematician; the other has a
PhD in a related discipline and more than 10 years experience studying
mathematical reasoning.)

>>>>

The data that underlie this section were generated in a series of online experiments in collaborative problem solving convened by mathematician Terence Tao \citeyearpar{tao2009imo,tao2011imo}.
\thesis{We use IATC to expand on a previous analysis of
  this data presented by \citet{pease-and-martin},} showing how IATC can
advance the theory of mathematical argument through the
detailed analysis of real world examples, as per \citet{Carrascal2015}.

In their 2012 paper,
Pease and Martin analysed the third MiniPolymath project in broad strokes,
with each blog comment comprising a single unit to be tagged.
They developed a typology of five intuitive comment types, based on
the mathematical content of each comment: \emph{examples},
\emph{conjectures}, \emph{concepts}, \emph{proofs}, and \emph{other}.
%%
In order to assign comments to these categories, both authors
performed close content analysis, together, on all comments posted
between the time at which Tao posted the problem to his blog
(8pm, UTC on July 19th, 2011) and the time he announced
that a solution had appeared (9.50pm, UTC on July 19th, 2011).
The discussion comprised 147 comments over 27 threads.
%%
Ten comments were assigned to more than one category.
(Both authors have a first degree in
Mathematics; one of us has a PhD in Mathematics and over 10 years
experience as a professional research mathematician; the other has a
PhD in a related discipline and more than 10 years experience studying
mathematical reasoning.)
